Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-07 ms/SI.Rmd
update

```{r, echo=TRUE}
library(jsonlite)
# for dependency
targets::tar_load(site_info)
#site <- fromJSON("../data/site_info.json")
site <- fromJSON("data/site_info.json")
site |>
  kable(format = "html") |>
  kable_styling()
```

| Site name  | Vegetation                             | Elevation (m) | Locations          | MAT (℃) | MAP (mm) | Dry period (month) | Canopy height (m) | Species number  |
|------------|----------------------------------------|---------------|--------------------|---------|----------|--------------------|-------------------|-----------------|
| Bubeng     | Tropical forest (TRF)                  | 780           | 21°37'N, 101°35' E | 21      | 1532     | 6                  | 35-45             | `r val$TRF`     |
| Ailao-shan | Subtropical evergreen wet forest (STF) | 2500          | 24°32'N,101°01'E   | 11.7    | 1931     | -                  | 25                | `r val$STF`     |
| Yuanjiang  | Hot-dry savanna  (HDS)                 | 480           | 23°28'N, 102°10'E  | 24.7    | 732.8    | 6                  | 4-6               | `r val$HDS`     |
| Yakushima  | Warm-temperate forest        | 14 - 1748     | 30°38'N, 130°62'E  | 19.4    | 4477     | -                  |       -            | `r val$yaku_sp` |

>>>>

```{r, echo=FALSE}
library(jsonlite)
# for dependency
targets::tar_load(site_info)
#site <- fromJSON("../data/site_info.json")
site <- fromJSON("data/site_info.json")
site |>
  kable(format = "html") |>
  kable_styling()
```
